SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/encoding.tex
intro-bio-encodingV6

\begin{align}
  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
\end{align}
Self edges are not allowed. 
\begin{align}
   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
\end{align}
\ankit{Without loss of generality, we can fix first half as Q-SNAREs and rest as R-SNAREs},
we set diagonal blocks in pairing matrix to be 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
\begin{align}
  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
  \tag{V6}\label{eq:c3}
\end{align}

@@

The key improvement in our work over the earlier tool is the
encoding of reachability, which was done using enumeration of paths.
%
In the current work, we have encoded reachability in two different
ways in formulas~\eqref{eq:reach1} and~\eqref{eq:drop3}.
%
The reachability is recursively defined in~\eqref{eq:drop3} and has
trivial solution by making all $r'$s true.
%
However, the trivial solution is disallowed by formula~\eqref{eq:drop4} and we find
only the solutions that captures the evidence of unreachability.
%
On the other hand,
we have added length of paths in our reachability encoding in formula~\eqref{eq:reach1},
which needs relatively more auxiliary variables.
%
This is because formula~\eqref{eq:reach2} has only positive
occurrences of the reachability variables and circular dependencies in
the recursive definition of $r'$s in ~\eqref{eq:reach1} may result
in spurious satisfying assignments that do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
formula remains polynomial in size, and satisfying assignments only
corresponds to correct reachability.

>>>>

\begin{align}
  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
\end{align}
Self edges are not allowed. 
\begin{align}
   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
\end{align}
We fix first half as Q-SNAREs and rest as R-SNAREs and set diagonal blocks in pairing matrix to be 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
\begin{align}
  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
  \tag{V6}\label{eq:c3}
\end{align}

@@

The key improvement in our work over the earlier tool is the
encoding of reachability, which was done using enumeration of paths.
%
In the current work, we have encoded reachability in two different
ways in formulas~\eqref{eq:reach1} and~\eqref{eq:drop3}.
%
The reachability is recursively defined in~\eqref{eq:drop3} and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by formula~\eqref{eq:drop4} and we find
only the solutions that captures the evidence of unreachability.
%
On the other hand,
we have added length of paths in our reachability encoding in formula~\eqref{eq:reach1},
which needs relatively more auxiliary variables.
%
This is because formula~\eqref{eq:reach2} has only positive
occurrences of the reachability variables and if we had defined
$r$s in ~\eqref{eq:reach1} without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
formula remains polynomial in size, and satisfying assignments only
correspond to correct reachability.
